07-logistic_regression

### 2019-03-05 journals/07-logistic_regression/07-logistic_regression.Rmd
more on logistic regression

The output from the model is shown below.

```{r}
# Summary of the model
summary(logistic_inters2)
```

### Comparing the Logistic Models

@@

```{r}
data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
  summarise_at(vars(mains, inters2), 
               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
               obs = hamby224_test %>% select(samesource) %>% na.omit())
```

@@

@@

```{r}
plot_features(lime_explain_mains$explain[1:12,])
hamby224_test %>% filter(case == 1)
```

>>>>

The output from this model is not shown.

```{r eval = FALSE}
# Summary of the model
summary(logistic_inters2)
```

### Comparing the Two Models

@@

```{r}
data.frame(obs = hamby224_test %>% 
             pull(samesource) %>% na.omit(),
           mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
  mutate(mains_sqerrs = (obs - as.logical(mains))^2,
         inters2_sqerrs = (obs - as.logical(inters2))^2) %>%
  summarise_at(vars(mains_sqerrs, inters2_sqerrs), 
               function(x) sum(x) / length(x)) %>%
  rename(mains_mse = mains_sqerrs, inters2_mse = inters2_sqerrs)
```

@@

### Default LIME Applied to Main Effects Model

@@

```{r}
plot_features(lime_explain_mains$explain[1:12,])
```

```{r}
coefs <- logistic_mains$finalModel$coefficients %>% round(2)
```

The logistic regression model is

$\log\left(\frac{\hat{p}}{1-\hat{p}}\right)=$ `r coefs[[1]]` + `r coefs[[2]]` ccf + `r coefs[[3]]` rough_cor + `r coefs[[4]]` D + `r coefs[[5]]` sd_D + `r coefs[[6]]` matches + `r coefs[[7]]` mismatches + `r coefs[[8]]` cms + `r coefs[[9]]` non_cms + `r coefs[[10]]` sum_peaks

where $\hat{p}=P(\mbox{samesource = TRUE})$.

I started trying to compare the results from LIME to the logistic regression model, but I realized that I need to standardize my test data before I use the model to make predictions.

```{r}
m = function(x) coefs[2:10] * x
m(hamby224_test[1,] %>% select(rf_features))
hamby224_test[1:4,] %>% select(rf_features)
coefs
hamby224_test[1:4,] %>% select(rf_features) * coefs[2:10]
```

```{r}
mains_test_explain <- hamby224_test %>%
  mutate(case = as.character(case)) %>%
  full_join(lime_explain_mains$explain, by = "case") %>%
  mutate(case = factor(case),
         feature = factor(feature))
```

Below is a plot of the three chosen features for each of the cases faceted by set. The features are ordered by order they were chosen by lime (ordered by magnitude of the coefficients).

```{r}
mains_test_explain %>%
  na.omit() %>%
  arrange(case, desc(abs(feature_weight))) %>%
  mutate(feature_order = rep(c("first", "second", "third"), n() / 3)) %>%
  select(case, set, feature, feature_order) %>%
  spread(feature_order, feature) %>%
  arrange(set, first, second, third) %>%
  mutate(order = 1:n()) %>%
  gather(feature_order, feature, 3:5) %>%
  ggplot(aes(x = feature_order, y = order, fill = feature)) + 
  geom_tile() + 
  facet_grid(set ~ ., scales = "free_y") +
  theme_bw() +
  gretchenalbrecht::scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  labs(x = "Order of Features Chosen", y = "Case", fill = "Feature")
```
